Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
Iter on the paper

\paragraph{The data matrix}
%
Blahblah

\paragraph{Supervised models: learning to predict}
%
Blahblah

>>>>

\paragraph{Setting up models and feeding them data}
%
Models in scikit-learn, called \emph{estimators}, are objects
instantiated with all parameters that describe them, but with data. They
have a {\tt fit} method, that accepts an $(n \times p)$ data
matrix--numpy array or scipy sparse matrix--, where $n$ is the number of
samples, and $p$ the number of features--, and possibly a quantity to
predict, also an array, 1D unless the prediction is \emph{multi-output},
with floats for a regression task, as in the wages prediction, or
integers for classification, that is predicting for each sample to which
class it belongs. The data seldom come in this form, and they must be
adapted to be suitable for consumption by estimators.

\paragraph{Supervised models: learning to predict}
%
The goal of supervised models is prediction; they
